**The status of the microbial census: an update**

### 2015-12-07 results/tables/build_archaeal_category_phylum_table.Rmd
Fix caption and table placement

**Supplementary Table 3. Frequency that each archaeal phylum was found across each of the environmental categories.**

@@

colnames(archaea) <- c("", categories)
composite <- xtable(archaea)

@@

print(composite, include.rownames=FALSE, include.colnames=TRUE, hline.after = c(-1,0,nrow(composite)-1, nrow(composite)), comment=FALSE, size="tiny", rotate.colnames=TRUE)

>>>>

\captionsetup{labelformat=empty}

@@

colnames(archaea) <- c("", categories)

colnames(archaea) <- paste0("\\textbf{", colnames(archaea), "}")

caption <- "\\textbf{Supplementary Table 3. Frequency that each archaeal phylum was found across each of the environmental categories.}"

composite <- xtable(archaea, caption=caption, label="")

@@

print(composite,
		include.rownames=FALSE,
		include.colnames=TRUE,
		hline.after = c(-1,0,nrow(composite)-1, nrow(composite)),
		comment=FALSE,
		caption.placement = "top",
		size="tiny",
		table.placement="!ht",
		rotate.colnames=TRUE
		)

### 2015-12-07 results/tables/build_archaeal_phylum_effort_table.Rmd
Fix caption and table placement

**Supplementary Table 5. Frequency that each archaeal phylum was sequenced before and after 2006.**

@@

data <- cbind(rownames(data), data)
colnames(data) <- c("Phylum",  "<2006 and Before", "After 2006", "Total", "Ratio of Ratios")

composite <- xtable(data)

@@

print(composite, include.rownames=FALSE, include.colnames=TRUE, hline.after = c(-1,0, nrow(composite)-1,nrow(composite)), comment=FALSE, size="normalsize")

>>>>

\captionsetup{labelformat=empty}

@@

data <- cbind(rownames(data), data)
colnames(data) <- c("\\textbf{Phylum}",  "\\textbf{<2006 and Before}", "\\textbf{After 2006}", "\\textbf{Total}", "\\textbf{Ratio of Ratios}")

caption <- "\\textbf{Supplementary Table 5. Frequency that each archaeal phylum was sequenced before and after 2006.}"

composite <- xtable(data, caption=caption, label="")

@@

print(composite,
	include.rownames=FALSE,
	include.colnames=TRUE,
	hline.after = c(-1,0, nrow(composite)-1,nrow(composite)),
	caption.placement = "top",
	comment=FALSE,
	table.placement="!ht",
	size="normalsize")

### 2015-12-07 results/tables/build_bacterial_category_phylum_table.Rmd
Fix caption and table placement

**Supplementary Table 2. Frequency that each bacterial phylum was found across each of the environmental categories.**

@@

colnames(bacteria) <- c("", categories)
composite <- xtable(bacteria)

@@

print(composite, include.rownames=FALSE, include.colnames=TRUE, hline.after = c(-1,0,nrow(composite)-1, nrow(composite)), comment=FALSE, size="tiny", rotate.colnames=TRUE)

>>>>

\captionsetup{labelformat=empty}

@@

colnames(bacteria) <- c("", categories)

colnames(bacteria) <- paste0("\\textbf{", colnames(bacteria), "}")

caption <- "\\textbf{Supplementary Table 2. Frequency that each bacterial phylum was found across each of the environmental categories.}"

composite <- xtable(bacteria, caption=caption, label="")

@@

print(composite,
	include.rownames=FALSE,
	include.colnames=TRUE,
	hline.after = c(-1,0,nrow(composite)-1, nrow(composite)),
	comment=FALSE,
	size="tiny",
	caption.placement = "top",
	table.placement="!ht",
	rotate.colnames=TRUE)

### 2015-12-07 results/tables/build_bacterial_culture_effort_table.Rmd
Fix caption and table placement

---
output:
  pdf_document:
    includes:
      in_header: table_header.tex
tables: true
geometry: margin=0.2in
---

@@

print(composite, include.rownames=FALSE, include.colnames=TRUE, hline.after = c(0, nrow(composite)-1, nrow(composite)), comment=FALSE, add.to.row=addtorow, caption.placement = "top", size="scriptsize")
```

>>>>

---
output:
  pdf_document:
    includes:
      in_header: table_header.tex
tables: true
geometry: margin=1.0in
---

@@

print(composite,
	include.rownames=FALSE,
	include.colnames=TRUE,
	hline.after = c(0, nrow(composite)-1, nrow(composite)),
	comment=FALSE,
	add.to.row=addtorow,
	caption.placement = "top",
	table.placement = "!ht",
	size="scriptsize")
```

### 2015-12-07 results/tables/build_bacterial_phylum_effort_table.Rmd
Fix caption and table placement

---
output:
  pdf_document:
    includes:
      in_header: table_header.tex
tables: true
geometry: margin=0.5in
---

**Supplementary Table 4. Frequency that each bacterial phylum was sequenced before and after 2006.**

@@

data <- cbind(rownames(data), data)
colnames(data) <- c("Phylum",  "<2006 and Before", "After 2006", "Total", "Ratio of Ratios")

composite <- xtable(data)

@@

print(composite, include.rownames=FALSE, include.colnames=TRUE, hline.after = c(-1,0, nrow(composite)-1, nrow(composite)), comment=FALSE, size="scriptsize")
```

>>>>

---
output:
  pdf_document:
    includes:
      in_header: table_header.tex
tables: true
geometry: margin=1.0in
---

\captionsetup{labelformat=empty}

@@

data <- cbind(rownames(data), data)
colnames(data) <- c("\\textbf{Phylum}",  "\\textbf{<2006 and Before}", "\\textbf{After 2006}", "\\textbf{Total}", "\\textbf{Ratio of Ratios}")

caption <- "\\textbf{Supplementary Table 4. Frequency that each bacterial phylum was sequenced before and after 2006.}"

composite <- xtable(data, caption=caption, label="")

@@

print(composite,
		include.rownames=FALSE,
		include.colnames=TRUE,
		hline.after = c(-1,0, nrow(composite)-1, nrow(composite)),
		comment=FALSE,
		caption.placement = "top",
		table.placement="!ht",
		size="scriptsize")
```

### 2015-12-07 results/tables/build_coverage_by_category.Rmd
Fix caption and table placement

**Table 1. Status of microbial census by habitat classifications and domain.** The isolation_source field from the SILVA reference database was manually curated to assign bacterial and archaeal sequences coarse and fine scale habitat classifications. We calculated the number of sequences and OTUs observed and the percent coverage on a sequence or OTU basis for each classification and domain.

@@

@@

composite <- xtable(composite)

addtorow <- list(pos=list(0, 1),
				command=c('\\multirow{4}{*}{Coarse} & \\multirow{4}{*}{Fine} & \\multicolumn{4}{c}{Bacteria} & \\multicolumn{4}{c}{Archaea} \\\\ \\cmidrule(r){3-6}	\\cmidrule(r){7-10}', '\\hline '))

align(composite) <- "lllcccccccc"
print(composite, add.to.row=addtorow, include.rownames=FALSE, include.colnames=FALSE, hline.after = c(-1,nrow(composite)-1, nrow(composite)), comment=FALSE, size="scriptsize")
```

>>>>

\captionsetup{labelformat=empty}

@@

header <- paste0("\\textbf{", header, "}")

caption <- "\\textbf{Table 1. Status of microbial census by habitat classifications and domain.}"
#The isolation_source field from the SILVA reference database was manually curated to assign bacterial and archaeal sequences coarse and fine scale habitat classifications. We calculated the number of sequences and OTUs observed and the percent coverage on a sequence or OTU basis for each classification and domain."

@@

composite <- xtable(composite, caption=caption, label="")

addtorow <- list(pos=list(0, 1),
				command=c('\\multirow{4}{*}{\\textbf{Coarse}} & \\multirow{4}{*}{\\textbf{Fine}} & \\multicolumn{4}{c}{\\textbf{Bacteria}} & \\multicolumn{4}{c}{\\textbf{Archaea}} \\\\ \\cmidrule(r){3-6}	\\cmidrule(r){7-10}', '\\hline '))

align(composite) <- "lllcccccccc"
print(composite,
	add.to.row=addtorow,
	include.rownames=FALSE,
	include.colnames=FALSE,
	hline.after = c(-1,nrow(composite)-1, nrow(composite)),
	comment=FALSE,
	caption.placement = "top",
	table.placement="!ht",
	size="scriptsize")
```

### 2015-12-07 results/tables/build_environmental_categories_table.Rmd
Fix caption and table placement

composite <- xtable(text, caption=caption, label="")
align(composite) <- "lllp{10cm}"
print(composite, include.rownames=FALSE, include.colnames=TRUE, hline.after = c(-1, nrow(composite)), comment=FALSE, add.to.row=addtorow, caption.placement = "top", size="scriptsize")
```

>>>>

composite <- xtable(text, caption=caption, label="")
align(composite) <- "lllp{10cm}"
print(composite,
		include.rownames=FALSE,
		include.colnames=TRUE,
		hline.after = c(-1, nrow(composite)),
		comment=FALSE,
		add.to.row=addtorow,
		caption.placement = "top",
		table.placement="!ht",
		size="footnotesize")
```
